Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-15 hscc2017/paper.tex
wording

By combining and applying state-of-the-art synthesis engines we present a
tool that automatically generates digital controllers for a given continuous
plant model that are correct by construction.  This approach presents a high
degree of autonomy, promises to reduce the cost and time of development of
digital control dramatically, and requires considerably less expertise than
a-posteriori verification methodologies.  Specifically, we synthesize
stable, software-implemented embedded controllers along with a model of a
physical plant.  Due to the complexity of such closed-loop systems, in this
work we focus on linear models with known configurations, and perform
parametric synthesis of stabilizing digital controllers (further closed-loop
requirements are left to future work).

Our work addresses challenging aspects of the control synthesis problem.  We
perform digital control synthesis over a hybrid model, where the plant
exhibits continuous behavior whereas the controller operates in discrete
time and over a quantized domain.  Inspired by a classical
approach~\cite{astrom1997computer}, we translate the problem into a single
digital domain.  Towards our goal of closed-loop stability, we have modeled
a digital equivalent of the continuous plant by evaluating the effects of
the quantizers (A/D and D/A converters) and of time discretization.  We
further account for uncertainties on the plant models.  The resulting
closed-loop system is a program loop that operates on bit-vectors encoded
using fixed-point arithmetic with finite word length (FWL).  The three
effects of 1.~uncertaities, 2.~FWL representation and 3.~quantization errors
are incorporated into the model, and are taken into account during the
CEGIS-based synthesis of the control software for the plant.

@@

\begin{mylemma}\cite{astrom1997computer}
%
Given a synchronized ZOH input and sample-and-hold output on the plant, 
with a sample time $T$ satisfying the Nyquist criterion, the discrete pulse
transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$, 
and can be computed using the following formula:
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = %\mathcal{ZOH}\left\lbrace{G(s)}\right\rbrace =
(1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
\end{mylemma}
%
For the sake of brevity, we will use the notation $G(z)$ to represent the
pulse transfer function $G(z,T)$.
% 
Lemma~\ref{eq:pulsetf} ensures that the poles and zeros match under the
$\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$
operations, and it includes the ZOH dynamics in the $(1-z^{-1})$ term. 
This is sufficient for stability studies over $G(s)$~\cite{fadali}, {\it i.e.}, if there is any unstable pole (in the complex domain $\Re\{s\} > 0$), 
the pulse transfer function in~\eqref{eq:pulsetf} will also present the same number of unstable poles ($|z| > 1$)~\cite{Franklin15}.

>>>>

By combining and applying state-of-the-art synthesis engines we present a
tool that automatically generates digital controllers for a given continuous
plant model that are correct by construction.  This approach delivers a high
degree of automation, promises to reduce the cost and time of development of
digital control dramatically, and requires considerably less expertise than
a-posteriori verification.  Specifically, we synthesize stable,
software-implemented embedded controllers along with a model of a physical
plant.  Due to the complexity of such closed-loop systems, in this work we
focus on linear models with known configurations, and perform parametric
synthesis of stabilizing digital controllers (further closed-loop
requirements are left to future work).

Our work addresses challenging aspects of the control synthesis problem.  We
perform digital control synthesis over a hybrid model, where the plant
exhibits continuous behavior whereas the controller operates in discrete
time and over a quantized domain.  Inspired by a classical
approach~\cite{astrom1997computer}, we translate the problem into a single
digital domain, i.e., we model a digital equivalent of the continuous plant
by evaluating the effects of the quantizers (A/D and D/A converters) and of
time discretization.  We further account for uncertainties in the plant
model.  The resulting closed-loop system is a program with a loop that
operates on bit-vectors encoded using fixed-point arithmetic with finite
word length (FWL).  The three effects of 1.~uncertaities, 2.~FWL
representation and 3.~quantization errors are incorporated into the model,
and are taken into account during the CEGIS-based synthesis of the control
software for the plant.

@@

\begin{mylemma}\cite{astrom1997computer}
%
Given a synchronized ZOH input and sample-and-hold output on the plant, 
with a sample time $T$ satisfying the Nyquist criterion, the discrete pulse
transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$, 
and can be computed using the following formula:
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = %\mathcal{ZOH}\left\lbrace{G(s)}\right\rbrace =
(1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
\end{mylemma}
%
For the sake of brevity, we will use the notation $G(z)$ to represent the
pulse transfer function $G(z,T)$.
% 
Lemma~\ref{eq:pulsetf} ensures that the poles and zeros match under the
$\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$
operations, and it includes the ZOH dynamics in the $(1-z^{-1})$ term.  This
is sufficient for stability studies over $G(s)$~\cite{fadali}, i.e., if
there is any unstable pole (in the complex domain $\Re\{s\} > 0$), the pulse
transfer function in~\eqref{eq:pulsetf} will also present the same number of
unstable poles ($|z| > 1$)~\cite{Franklin15}.
